---
title: "MA213 Basic Statistics and Probability - Lab3 Activity"
bibliography: references.bib
link-citations: true
output:
  html_document:
    code_download: true 
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

## **Lab 3:** **Plotting and Summaries** activities

------------------------------------------------------------------------

### **New York Air Quality Dataset**

#### Q0. Import the `airquality.csv` file.

```{r}
#
#
# 
df <- read.csv("airquality.csv")
head(df)
names(df)
```

#### Q1. You are interested in Ozone level excluding May. You want to see how Ozone level is distributed in June, July, August and September by looking at a plot.

```{r}


```

#### Q3. You want to see how average speed of wind changes over time (Month). Can you visualize it?

```{r}


```

#### Q4. Do you see any patterns of level of Ozone over time?

```{r}



```

#### Q5. Show the scatter plot of Solar radiation and Temperature.

```{r}
#
#
#

```

#### Show the bar plot of average Solar radiation per each month.

```{r}
#
#
#

```

### **Survival of Passengers on the Titanic**

#### Import the `titanic.csv` file.

```{r}
#
#
#

```

#### You are interested in how the data is categorized by sex visually. Show the pie chart of `sex`

```{r}
#
#
#
```

#### You are interested in whether sex is related to survival in the Titanic disaster. How would you visualize or summarize this relationship?

```{r}
#
#
#
```

#### You are also interested in exploring whether age is associated with survival. How would you go about visualizing or summarizing this relationship?

```{r}
#
#
#
```

### Post-lab activities

Please name your submission as `lab3.R`

We are going to also analyze this New York Air Quality Measurements data again. This time, we are going to see how Solar radiation is behaving with Temperature.

1.  load the `airquality.csv` file and assign it to `my_df` object.

2.  Show the scatter plot of Solar radiation and Temperature.

3.  Show average Solar radiation in each month. Use bar plot.

    2.1) Assign average Solar radiation into object `solar_radiation_avg` .

    2.2) Show the bar plot of average Solar radiation per each month.

Back to Titanic data.

1.  Show the pie chart of `sex` in `titanic` data.

    3.1) Load `titanic.csv` file and assign it to `my_df2` object.

    3.2) Show the pie chart of `sex` .

### References
