%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lesson Plan (50 minutes)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{Lesson Plan}
    \begin{itemize}
        \item xx min Lecture: motivate using ANOVA to compare means across 3+ groups, maybe using an example to return to throughout the lecture
        \item xx min Lecture: compare z/t test vs ANOVA (like slides 5-9)
        \item xx min Edfinity quiz: in our lecture example, how would you set up the hypotheses?
        \item xx min Lecture: explain the ANOVA test statistic, sum of squares between groups/total/error, mean squared error
        \item xx min R Demonstration: Compute the ANOVA table up to the test statistic. Then simulate the shape of the distribution under the null hypothesis and plot the F distribution on top. Use the theoretical distribution to compute the p-value
        \begin{itemize}
            \item Highlight concepts of: between-group and within-group variability 
        \end{itemize}
        \item xx min Lecture: p-value
        \item xx min Edfinity quiz: now with all the tools in hand, conduct an ANOVA test, step-by-step
        \item xx min R Demonstration: answers to the quiz in R
        \item xx min Lecture review and interpretation of the test results
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Learning objectives:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{Learning Objectives}
    \begin{itemize}
        \item \textbf{M1, LO3: Use R for Data Management and Exploration:} Utilize R to load, pre-process, and explore data through visualization and summarization techniques.
        \item \textbf{M3, LO1: Understand Point Estimates and Sampling Variability:} Define a sample statistic (point estimate) for a population parameter, and explain how it varies across different samples.
        \item \textbf{M3, LO3: Calculate and Interpret Standard Error:} Calculate the standard error for proportions and interpret it as a measure of sampling variability.
        \item \textbf{M3, LO4: Explain Hypothesis Testing and Its Limitations:} Discuss the use cases and potential issues with hypothesis testing, including the interpretation of results.
        \item \textbf{M3, LO6: Distinguish Statistical vs. Practical Significance:} Differentiate between statistical significance and practical significance, and explain the implications of each.
        \item \textbf{M4, LO2: Design and Interpret Confidence Intervals:} Design, execute, and interpret confidence intervals for the population proportion.
        \item \textbf{M4: LO8: Conduct and Interpret ANOVA:} Assess whether conditions for an ANOVA are met, and if so, design, execute, and interpret the test to compare sample means across several groups.
    \end{itemize}
\end{frame}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO: Combine slides on ANOVA
% TODO: Edfinity quiz on setting up the hypotheses
% TODO: R demo: ANOVA table for example, simulation to show shape of F distribution, calculate p-value
% TODO: Edfinity quiz: ANOVA, step by step
% TODO: R demo: quiz answers

