---
title: "MA213 Basic Statistics and Probability - Lab1 Activity"
output:
  pdf_document: default
  html_document:
    code_download: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

## **Lab 1: Introduction to R** 

------------------------------------------------------------------------

## Lab Activities

#### Q1. Let's set up your working directory.

```{r, echo=TRUE}

#

```

#### Q2. Use R commands to calculate the following and print `C` .

$A = \exp(3),$ $B = \frac{(-3)^{4}}{10},$

$C = A \times B$

```{r, echo=TRUE}
#


```

#### Q3. You are going to explore the data extracted from the 1974 *Motor Trend* US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

You can look at the description of the data by `help(mtcars)` .

Please remember to use `help()` function or `?function_name` method. You are going to use it a lot when you use R.

Here are some useful functions for vectors.

`length(x)` : get the length of vector `x`

`unique(x)` : get the unique values of vector `x`

`min(x)` : get the minimum value of vector `x`

`max(x)` : get the maximum value of vector `x`

`mean(x)` : get the mean (average) of vector `x`

Import `mtcars.csv` to `cars_data`

```{r}
#


```

#### Q4. You are interested in first five data (first five rows). Assign first five rows to `cars_data_5` and print it.

```{r}
#


```

#### Q5. You are interested in cars with horsepower greater than 100. Show the cars that have horsepower greater than 100.

```{r}
#

```

#### Q6. This time, you are only interested in 4 cylinder cars with gross horsepower(5th column) and weight in 1000lbs (7th column). Show it! (You need to show `cyl`, `hp` and `wt` column which are 3rd, 5th and 7th column).

```{r}
#

```

#### Q7. You are interested in the total sum of horse power and the average of mils per gallon of all the cars in the data. Assign them to `hp_sum` and `mpg_mean`. You can use `sum()` function and `mean()` function.

```{r}
#

```

------------------------------------------------------------------------

## Post-lab activities

Please name your submission as `lab1.R` on GradeScope.

1.  Calculate these questions and assign the answers to the corresponding variables.

a). $$a=\frac{45}{9}$$

b). $$ b=25^{4}$$

c). $$ c=\exp(-10) $$

For example, you would write a line of code as the following

``` r
a <- 45/9
```

2.  In `mtcars.csv` data,

    Import `mtcars.csv` to `cars_data` , you are only interested in automatic transmission cars with weight over 3000 lbs. Assign it to `cars_data_sub` (You need to get `cars_data` and `cars_data_sub`).

3.  You are interested in how many different number of cylinders of the cars in the datasets. You can count them and distinguish them in this dataset. However, if it is a large data, it is not possible to do it manually. Assign unique number of cylinders of the cars in the data by using `unique()` function and assign it to variable `unique_cyl` .
