%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lesson Plan (50 minutes)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{Lesson Plan}
    \begin{itemize}
        \item xx min Lecture: ANOVA review. Which means differ? Motivate multiple comparisons
        \item xx min R demo: multiple testing type I error, introduce concept of familywise error rate
        \item xx min Board work: derive familywise error rate for independent tests
        \item xx min Edfinity quiz: how to choose alpha to control FWER?
        \item xx min R demo: multiple testing with Bonferroni
        \item xx min Lecture: Go through t tests for ANOVA example
        \item xx min Case study: Garden of forking paths, statistical vs practical significance
        \item xx min Lecture: Best practices (avoid HT when inappropriate, preregistration, report effect size and CIs, data splitting for exploratory work)
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Learning objectives:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{Learning Objectives}
    \begin{itemize}
        \item \textbf{M1, LO3: Use R for Data Management and Exploration:} Utilize R to load, pre-process, and explore data through visualization and summarization techniques.
        \item \textbf{M3, LO1: Understand Point Estimates and Sampling Variability:} Define a sample statistic (point estimate) for a population parameter, and explain how it varies across different samples.
        \item \textbf{M3, LO3: Calculate and Interpret Standard Error:} Calculate the standard error for proportions and interpret it as a measure of sampling variability.
        \item \textbf{M3, LO4: Explain Hypothesis Testing and Its Limitations:} Discuss the use cases and potential issues with hypothesis testing, including the interpretation of results.
        \item \textbf{M3, LO6: Distinguish Statistical vs. Practical Significance:} Differentiate between statistical significance and practical significance, and explain the implications of each.
        \item \textbf{M4, LO2: Design and Interpret Confidence Intervals:} Design, execute, and interpret confidence intervals for the population proportion.
        \item \textbf{M4: LO8: Conduct and Interpret ANOVA:} Assess whether conditions for an ANOVA are met, and if so, design, execute, and interpret the test to compare sample means across several groups.
    \end{itemize}
\end{frame}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO: Make this lecture 30
% TODO: R demo simulating multiple testing with no effect
% TODO: Prep board work deriving FWER
% TODO: Edfinity quiz: adjusting alpha brainstorm
% TODO: Find a good case study for garden of forking paths, statistical vs practical significance (e.g. look at Gelman blog), prep it
% TODO: Prep lecture slides on garden of forking paths, best practices