%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lesson Plan (50 minutes)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{Lesson Plan}
    \begin{itemize}
        \item xx min Lecture: review linear model, $R^2$, extrapolation from last time
        \item xx min Lecture: motivate and then define outliers
        \item xx min R Demonstration: how do influential points change the best-fit lines?
        \item xx min Edfinity: outliers applet?
        \item xx min Lecture and/or R Demonstration: what to do with or how to address outliers (?)  % not in slides but feels missing? (ES: I agree. I think the answer is to run the regression with/without, and explain to the stakeholders as necessary. Is there more to it than that?)
        \item xx min Lecture/Case Study: Telling a story with statistics and when statistics can be misleading, statistical ethics
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Learning objectives:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{Learning Objectives}
    \begin{itemize}
        \item \textbf{M1, LO1: Classify and Analyze Variables:} Categorize variables based on their types (e.g., numerical/categorical, continuous/discrete, ordinal), assess their association (positive, negative, or independent), and determine which make sense as explanatory vs. response variables.
        \item \textbf{M1, LO3: Use R for Data Management and Exploration:} Utilize R to load, pre-process, and explore data through visualization and summarization techniques.
        \item \textbf{M1, LO4: Visualize and Describe Data Distributions:} Select appropriate visualizations (scatterplots, histograms, box plots, bar plots) to depict data, and describe distributions qualitatively (shape, center, spread, outliers) and quantitatively (mean, median, mode, range, IQR, standard deviation).
        \item \textbf{M5, LO1: Describe and Assess Relationships Between Two Variables:} Describe the association between two numerical variables in a scatter plot in terms of direction, shape (linear or nonlinear), and strength, and assess whether linear regression is an appropriate model.    
        \item \textbf{M5, LO2: Compute and Interpret Correlation and R²:} Compute and interpret correlation coefficients and R² values, while recognizing that correlation does not imply causation. 
        \item \textbf{M5, LO3: Fit and Interpret Linear Models Using Least Squares:} Fit the intercept and slope of a linear model to data using the least squares method, interpret the fitted values, and use the model to predict responses to new inputs.
        \item \textbf{M5, LO4: Explain and Assess Model Fit:} Explain the least squares fitting procedure, assess whether the fit is unduly influenced by any particular points, and distinguish between interpolation and extrapolation in predictions.
    \end{itemize}
\end{frame}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO: R demo on influential points and the best-fit line
% TODO: look for applets on outliers in regression, use for edfinity activity?
% TODO: Lecture / R demo on how to address outliers
% TODO: Lecture / Case Study on misleading statistics, statistical ethics