---
title: "MA213 Basic Statistics and Probability - Lab2 Activity"
bibliography: references.bib
link-citations: true
output:
  pdf_document: default
  html_document:
    code_download: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Lab 2:** Data transformation

------------------------------------------------------------------------

## Load packages for Data

If you didn't install `tidyverse` package

```{r eval=FALSE}
install.packages("tidyverse")
```

Load package

```{r, echo=TRUE}
library(tidyverse)
```

------------------------------------------------------------------------

## Lab Activities

#### Q1. Import `airquality` data. Discuss which variable should be response variable and explanatory variables. You might consider using functions such as `glimpse(), head()`

```{r}
#
# 
# 
```

#### Q2. You are interested in viewing temperature in Celsius. Create a column named `Temp_C`. Below is the formula for Celsius.

$$
C = (F-32) \times \frac{5}{9}
$$

```{r}
#
#
# 
```

#### Q3. Show average Ozone level in each month.

```{r}
#
#
# 
```

#### Q4. Based on Beaufort wind scale, wind speed(mph) can be categorized into

```         
Calm: Wind speed less than 1 mph. 
Light Air: 1-4 mph. 
Light Breeze: 4-7 mph. 
Gentle Breeze: 7-12 mph. 
Moderate Breeze: 12-18 mph. 
Fresh Breeze: 18-24 mph. 
Strong Breeze: Wind speed greater than 24 mph.
```

Also, we can categorize Ozone level into two levels as the following.

```         
Low : if less than median of Ozone
High : if greater than median of Ozone
```

Create a contingency table to examine the relationship between Categorized_wind and Ozone level.

```{r}
#
#
#

```

#### Q5. Import the Titanic dataset, identify numerical and categorical variables, and discuss which variable should be the response variable and which should be the explanatory variables.

```{r}
#
#
# 
```

#### Q6. Create a contingency table to examine the relationship between Class and Survived.

```{r}
#
#
#
```

#### Q7. Create a contingency table to examine the relationship between Sex and Survived.

```{r}
#
#
#
```

## Post-lab activities

Please name your submission as `lab2.R`

We are going to analyze this New York Air Quality Measurements data again. This time, we are going to see how Solar radiation is behaving in terms of Temperature.

We are going to work without missing values again.

0.  load the `airquality.csv` file and assign it to `my_df` object. And assign the data without `NA` value to `new_df`

    ```{r, eval=FALSE}
    my_df <- read.csv("airquality.csv")
    # new_df <- ?
    ```

1.  How many observations are in the data without missing value? In other words, how many rows in the data without missing value? Assign it to `n`

2.  What is the maximum daily temperature at LaGuardia airport? Assign it to `max_temp`

3.  What is the maximum Ozone(ppb) in month of June? Assign it to `max_ozone_june`

4.  You are interested in the median value of `wind` in August. Assign the value to `median_august_wind`
